\sys: Automated Data-Parallel Shell Processing

### 2020-04-24 pldi/draft.tex
New figures with eager and no-eager results
Some notes on the paper draft

\tr{Remember to mention the assumptions that need to hold for the
  graph transformations to be valid in the Command categories
  section. Commands must be deterministic, they must not do any other
  side effect (such as writing to other files, sending signals,
  etc). However, these assumptions must already be checked when the
  developer designates the categories.}

@@

\TODO{Explain the plots with eager/no-eager as follows. Say that we
  initially decided to only make an eager version of cat (to allow for
  parallelism). However, we saw that results are still not good, so we
  resorted to making a proper generic eager node that can be put
  anywhere in the graph and that eagerly consumes its input. The above
  results show the improvement with it. Rerun them with eager only
  before cat in the no eager cases to showcase the above
  results. (Maybe) we need to mention that eager has disk usage
  overhead that is linear to the size of the pipeline and the size of
  the input.}

>>>>

\kk{Remember to mention the assumptions that need to hold for the
  graph transformations to be valid in the Command categories
  section. Commands must be deterministic, they must not do any other
  side effect (such as writing to other files, sending signals,
  etc). However, these assumptions must already be checked when the
  developer designates the categories. Commands are assumed to always
  terminate gracefully. \sys changes the termination behaviour of
  commands as a sequential command that would exit prematurely might
  not exit completely if parallelized.}

@@

\TODO{Explain the plots with eager/no-eager as follows. Say that we
  initially decided to only make an eager version of cat (to allow for
  parallelism). However, we saw that results are still not good, so we
  resorted to making a proper generic eager node that can be put
  anywhere in the graph and that eagerly consumes its input. The above
  results show the improvement with it. Rerun them with eager only
  before cat in the no eager cases so that the minimal-grep example is
  the same with and without our eager node. (Maybe) we need to mention
  that eager has disk usage overhead that is linear to the size of the
  pipeline and the size of the input.}
